---
title: "Getting Started with SpotifyAssistantR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting-Started-with-SpotifyAssistantR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SpotifyAssistantR)
```

## SpotifyAssistantR
This package uses wrapper functions from the Spotify API and `SpotifyR` and combines them to give Spotify users more insight about their listening habits. It has four main functions:
1. Getting the most recent song releases by continent
2. Getting the user's top genres
3. Getting the user's playlists and tracks
4. Getting new song recommendations based on the user's top artists

## Initial Setup
In order to use the `SpofityAssistantR` package, the user must have a Spotify account, as well as a Spotify Developer Account.
[Click here](https://developer.spotify.com/dashboard/login) to create a Spotify Developer account.

### Client ID and Secret
Once the developer acount has been made, login and go to the user `Dashboard`. 
Click on the green `CREATE AN APP` button and name the new app.
Once the app has been created, the user will be immediately redirected to the app overview page.
On this page, directly under the name of the app, there are some pieces of information.
Note down the `Client ID`. This is one of the two credentials necessary for using the functions in this package.
The `Client ID` should be set as a System Environment variable, as in the following:

```{r, eval=FALSE}
Sys.setenv(SPOTIFY_CLIENT_ID = 'xxxxxxxxxxxxxxxxxxxxx')
```

Click on `SHOW CLIENT SECRET`. Note down `Client Secret`. This is the other credential necessary 
for using the functions in this package. It should also be set as a System Environment variable, as in the following:

```{r, eval=FALSE}
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'xxxxxxxxxxxxxxxxxxxxx')
```

Please note that these two credentials should be confidential, and they are unique to the app.

### Redirect URI
In the app overview page, aside from the Client ID and Secret information, there is one more part to the setup process.
Click on the green `EDIT SETTINGS` button on the right side of the page. Add the following as a `Redirect URI`:

`http://localhost:1410/` 

Now the setup process is complete.

## Getting New Releases by Continent
The following function will return one album from the Americas (i.e. North and South America)

```{r, eval=FALSE}
get_new_releases_by_continent('Americas', 1)
```

## Getting User Top Genres
The following function will return the user's top genres based on their listening trends:

```{r, eval=FALSE}
get_users_top_genres()
```

## Getting User Playlists and Tracks
The following function will return the user's playlists and tracks:

```{r, eval=FALSE}
get_playlists_songs()
```

## Getting User Song Recommendations
The following function will create a new playlist on Spotify, containing recommended songs for the user based on the user's top artists. It is possible to specify a name for the new playlist using the `playlist_name` arugment. If this is left blank, the playlist will simply be named "Recommended Songs" followed by the current date. 
The user can also specify the number of songs to return in the playlist using the `num_songs` argument. The default is 10 songs.

```{r, eval=FALSE}
get_song_recommendations()
```

